\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-22 manuscript.tex
edits
edits

\clearpage
\footnotetext{\flushleft{Manuscript received \line(1,0){120};   revision accepted\line(1,0){120}.}
\vspace*{1cm}
\subsection*{Acknowledgements}
Place brief acknowledgments, if desired, as a separate paragraph, using the following style: “The author(s) thank(s)…”. For brevity, do not use first names. Include grant acknowledgments here.
}
\clearpage

@@

\emph{Key results:} Genotyping results suggest the \emph{Hopscotch} element is at higher than expected frequency in teosinte. Analysis of linkage disequilibrium near \emph{tb1} does not support recent introgression of the \emph{Hopscotch} allele from maize into teosinte.  Population genetic signatures are consistent with selection on this locus revealing a potential ecological role for \emph{Hopscotch} in teosinte. Finally, two greenhouse experiments with teosinte do not suggest \emph{tb1} controls tillering in natural populations.

@@

\textbf{Key words:} domestication; maize; teosinte; \emph{teosinte branched1}; QTL \lev{??}  \mbh{not sure about QTL...might make people think we've done some QTL mapping which we haven't}

>>>>

\clearpage
\footnotetext{\flushleft{Manuscript received \line(1,0){120};   revision accepted\line(1,0){120}.}
\vspace*{1cm}
\subsection*{Acknowledgements}
Place brief acknowledgments, if desired, as a separate paragraph, using the following style: “The author(s) thank(s)…”. For brevity, do not use first names. Include grant acknowledgments here.
}

\lev{Grants as far as I know were Matt's UC Mexus money, whatever money paid for the 55K data since we used that, and I am not sure what paid for greenhouse space}
\clearpage

@@

\emph{Key results:} Genotyping results suggest the \emph{Hopscotch} element is at higher than expected frequency in teosinte. Analysis of linkage disequilibrium near \emph{tb1} does not support recent introgression of the \emph{Hopscotch} allele from maize into teosinte.  Population genetic signatures are consistent with selection on this locus revealing a potential ecological role for \emph{Hopscotch} in teosinte. Finally, two greenhouse experiments with teosinte do not suggest \emph{tb1} controls tillering in natural populations. \lev{do you think that we could change this at all to say something to make it sound less like hopscotch has absolutely no effect? I think it's likely that it was something with our experiments, or that it is the effect of other loci}

@@

\textbf{Key words:} domestication; maize; teosinte; \emph{teosinte branched1};
